\documentclass[a4paper, 12pt]{article}
\usepackage[english]{babel}
\usepackage{graphicx, ctable, url}
\usepackage{hyperref}
\usepackage{eurosym}
\usepackage{listings} % source listings
\lstloadlanguages{java}
\lstset{keywordstyle=\ttfamily\bfseries}
\lstset{flexiblecolumns=true}
\lstset{commentstyle=\ttfamily\itshape}

	\begin{document}

\title{Minutes Meeting 19}
\author{Wouter Van Rossem}
\date{\today}

\maketitle	
	\section{Meeting Information}
		\textbf{Date:} Wednesday, March 31, 2010\\
		\textbf{Time:} 16H00--16H30\\
		\textbf{Place:} Infogroep\\
		\subsection{Attendees}
Following members were present:
			\begin{itemize}
				\item Nick De Cooman
				\item Jonathan Jeurissen
				\item Bart Maes
				\item Jorne Laton
				\item Patrick Provinciael
				\item Wouter Van Rossem
				\item Sina Khakbaz Heshmati
			\end{itemize}

%Following members were absent:
%			\begin{itemize}
			 
%			\end{itemize}
			
		\subsection{Revision History}
			\begin{tabular}{c | l | l }
				\textbf{Rev.} & \textbf{Date} & \textbf{Description} \\
				\hline
				1.0 & April 4, 2010 & First draft created \\
				%1.1 & March 10, 2010 & Revised by QA Manager \\
			\end{tabular}		

	\section{Evaluation of conference}
		\subsection{Evaluation of our presentation}
			First we discussed our own presentation.
			\begin{description}
				\item[Part 1] There were some minor flaws in Sina's presentation. He didn't address all the items as discussed in the preparation meetings. Also, because Dutch is not his native tongue, the tempo of the presentation was a bit low. Therefore it would be better if next time he did his presentation in English.
				\item[Part 2] The overall impression of the group was positive for the demo.
				\item[Part 3] This part was also considered positive by the group. However, one improvement for next time would be that the discussed items should be linked with previous events.
			\end{description}
			Also, in the next conference we should lay more emphasis on what we have learned, since it seamed that this interested prof. Vermeir.

		\subsection{Impressions and comments on other groups}
		Group 3:
		\begin{itemize}
			\item The impression that our group got, was that it seams that they just want a working website, but aren't really interested in exploring new technologies
			\item Currently their website also doesn't look robust, since they did not show any invalid input.
			\item The way they did their demo (on person giving the demo and another person performing actions in the background) was a nice idea.
			\item The diagram with the amount of hours worked on the different tasks during both semesters was considered a nice idea as well.
		\end{itemize}
		Groep 1:
		\begin{itemize}
			\item The fact that the project manager of this group was absent didn't feel very professional. 
			\item	 The functionality of their website seems to resembles ours somewhat.
			\item They laid a lot of focus on the css of their website.
			\item The amount of hours worked on their timesheets is rather low compared to the other groups.
		\end{itemize}

	\section{Planning Easter Holiday}
		During the Easter Holiday we will focus on updating the documents, but also continue implementing. Sina will create a new division of labour for this. The amount of time spent on quality assurance should also be reduced from now on.
	
	
	\section{Agenda}
A complete list of Agenda items is available on \cite{agendaitems}.\\
	
	\begin{thebibliography}{99}
		
		\bibitem{agendaitems}
		\href{http://code.google.com/p/salesmen/wiki/NextMeetingTopics}{http://code.google.com/p/salesmen/wiki/NextMeetingTopics}
		
	\end{thebibliography}	
		
\end{document}
