\documentclass[a4paper, 12pt]{article}
\usepackage[english]{babel}
\usepackage{graphicx, ctable, url}
\usepackage{hyperref}
\usepackage{eurosym}
\usepackage{listings} % source listings
\lstloadlanguages{java}
\lstset{keywordstyle=\ttfamily\bfseries}
\lstset{flexiblecolumns=true}
\lstset{commentstyle=\ttfamily\itshape}

	\begin{document}

\title{Minutes Meeting 12}
\author{Wouter Van Rossem}
\date{\today}

\maketitle	
	\section{Meeting Information}
		\textbf{Date:} Friday, December 11, 2009\\
		\textbf{Time:} 12H00--13H00\\
		\textbf{Place:} CSB Seminaryroom 1\\
		\subsection{Attendees}
Following members were present:
			\begin{itemize}
				\item Nick De Cooman
				\item Sina Khakbaz Heshmati
				\item Bart Maes
				\item Wouter Van Rossem
			\end{itemize}
Following members were excused:
			\begin{itemize}
				\item Jonathan Jeurissen due to extra class
				\item Patrick Provinciael due to sickness
			\end{itemize}
Jorne Laton	was absent.		
			
		\subsection{Revision History}
			\begin{tabular}{c | l | l }
				\textbf{Rev.} & \textbf{Date} & \textbf{Description} \\
				\hline
				1.0 & December 12, 2009 & First draft created \\
				1.1 & December 13, 2009 & Revision by project manager \\
				1.2 & December 14, 2009 & Revised by QA manager \\
				1.3 & December 20, 2009 & Revised by Project Assistant \\
				

			\end{tabular}		
	
	\section{Timesheets}
References in the timesheets for the preparation for the first conference will be put online after the conference. Meanwhile, ``This reference will be put here after the conference" will be put as a reference for these items.

	\section{New versions of the documents}
New versions of the following documents will be put online before the conference:
		\begin{itemize}
			\item SRS
			\item SCMP
			\item SPMP
			\item SQAP
		\end{itemize}
		
	\section{Comparison documents of other groups}
Each team member will check the documents he has written with the corresponding documents of the other groups. If this has already been done, he will check for updates to these documents.

	\section{Workshop by Sina on implementation}
Next, Sina gave a tutorial on how to use Seam in Eclipse. Nick will also write a summary of this on the wiki. 

	\section{Implementation}
Before the implementation can begin, a revision of the design is needed. More complete coding conventions should also be determined.	
	
	\section{Next Meeting}

		\textbf{Date:} Tuesday, December 15, 2009\\
		\textbf{Time:} 14H00--15H00\\
		\textbf{Place:} E3.06\\
	
		\subsection{Agenda}
A complete list of Agenda items is available on \cite{site6}.\\
	
	\begin{thebibliography}{99}
		\bibitem{site6}
		\href{http://code.google.com/p/salesmen/wiki/NextMeetingTopics}{http://code.google.com/p/salesmen/wiki/NextMeetingTopics}

		
	\end{thebibliography}	
		
\end{document}
