\documentclass{article}

\usepackage{hyperref}

\begin{document}

	\title{Software Engineering Group 2 (2009-2010) \\ Highlights December 2009}
	\author{Nick De Cooman}
	\date {\today}

\maketitle

This report intends to give an overview of recent developments and improvements in order to provide some information about the progress of the Salesmen Project. A more detailed view on the status of this project can be obtained by looking at the timesheets \cite{timesheets}. \\
\\
This month we have been working on:

\begin{itemize}
	
	
\item \textbf{Presentation on conference} \\
  Focussing on the conference on December 15, two extra meeting were held in order to prepare our presentation. Afterwards, all documents \cite{conference} related to the conference were published on our project website. 
  
\item \textbf{Publishing the STD} \\
  This document \cite{std} outlines the various tests and testing procedures required for the Salesmen Project. It was released on December 6.
  
\item \textbf{Start coding} \\
  Since our choice for Seam, the initial design had to be slightly adapted to 
  support the Seam framework. On December 19, the implementation tasks were 
  distributed \cite{tasks} by the implementation manager. Currently, 
  our application provides some basic functionality. What's more, all team 
  members have learned to work with Seam, which was set as our main target. 
  To track our coding progress, we use the issue tracking system \cite{issues}
  provided by Google code and Twitter \cite{twitter} to report our activities. 

\item \textbf{Unification of all documents} \\
  All documents were re-published to reflect unification of styles. At the same time, a new version of every document was released.
\end{itemize}

\begin{thebibliography}{99}

	\bibitem{timesheets}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/timesheets/}{http://wilma.vub.ac.be/~se2_0910/docs/timesheets/}
		
	\bibitem{conference}
	\href{http://wilma.vub.ac.be/~se2_0910/dev/events/2009/vub-se/}{http://wilma.vub.ac.be/~se2_0910/dev/events/2009/vub-se/}
	
	\bibitem{std}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/std/}{http://wilma.vub.ac.be/~se2_0910/docs/std/}

	\bibitem{tasks}
	\href{http://code.google.com/p/salesmen/wiki/DevelopmentRoles}{http://code.google.com/p/salesmen/wiki/DevelopmentRoles}
	
	\bibitem{issues}
	\href{http://code.google.com/p/salesmen/issues/list}{http://code.google.com/p/salesmen/issues/list}
	
	\bibitem{twitter}
	\href{http://twitter.com/salesmendev}{http://twitter.com/salesmendev}
	
	
\end{thebibliography}


\end{document}
