\documentclass{article}

\usepackage{hyperref}

\begin{document}

	\title{Software Engineering Group 2 (2009-2010) \\ Highlights November}
	\author{Nick De Cooman}
	\date {\today}

\maketitle

This report intends to give an overview of recent developments and improvements in order to provide some information about the progress of the Salesmen Project. A more detailed view on the status of this project can be obtained by looking at the timesheets \cite{timesheets}. \\
\\
This month we have been working on:

\begin{itemize}
	
	
	\item \textbf{Specifying requirements in SRS} \\
	In order to define the functionality of the system, several meetings were held to discuss possible requirements. On November 12, we were finally able to release a first version of the SRS \cite{srs} which intends to present an overall description and listing of the functionality of the system behind the Salesmen Project.
	
	\item \textbf{Publishing the SCMP} \\
	This document \cite{scmp} is intended to describe how the Salesmen project artifacts are stored, processed, and deployed. It was released on November 8 by the configuration team. 
	
	\item \textbf{Focussing on quality assurance} \\
	By having a presentation on the quality assurance and releasing the SQAP \cite{sqap} on November 22, directives were given to ensure quality to all team members.
	
	\item \textbf{Updating SPMP} \\
Version 0.2 of the SPMP \cite{spmp} has been released on November 28 and now meets the requests of the customer. It also includes an estimation of costs, a detailed planning and a reviewed risks analysis. 
	
	\item \textbf{Releasing SDD} \\
	On November 30, the SDD \cite{sdd} was released which describes the software architecture and design for the initial release of the Salesmen software. The design decisions directly relate to the functionalities, performances, constraints, attributes and interfaces of the system.
	
	\item \textbf{Preparing conference on 15/12} \\
	In order to organise the presentation on the conferene, we scheduled extra meetings.
		
\end{itemize}
  

\begin{thebibliography}{99}

	\bibitem{timesheets}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/timesheets/}{http://wilma.vub.ac.be/~se2_0910/docs/timesheets/}
	
	\bibitem{srs}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/srs/}{http://wilma.vub.ac.be/~se2_0910/docs/srs/}
	
	\bibitem{scmp}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/scmp/}{http://wilma.vub.ac.be/~se2_0910/docs/scmp/}
	
	\bibitem{sqap}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/sqap/}{http://wilma.vub.ac.be/~se2_0910/docs/sqap/}

	\bibitem{spmp}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/spmp/}{http://wilma.vub.ac.be/~se2_0910/docs/spmp/}
	
	\bibitem{sdd}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/sdd/}{http://wilma.vub.ac.be/~se2_0910/docs/sdd/}	
	
	
\end{thebibliography}


\end{document}