\documentclass[a4paper, 12pt]{article}
\usepackage[english]{babel}
\usepackage{graphicx, ctable, url}
\usepackage{hyperref}
\usepackage{eurosym}
\usepackage{listings} % source listings
\lstloadlanguages{java}
\lstset{keywordstyle=\ttfamily\bfseries}
\lstset{flexiblecolumns=true}
\lstset{commentstyle=\ttfamily\itshape}

	\begin{document}

\title{Minutes Conference Meeting 1}
\author{Nick De Cooman}
\date{\today}

\maketitle	
	\section{Meeting Information}
		\textbf{Date:} Friday, November 27, 2009\\
		\textbf{Time:} 12H00--13H00\\
		\textbf{Place:} CSB Seminaryroom 2\\
		
		\subsection{Attendees}
Following members were present:
			\begin{itemize}
				\item Nick De Cooman
				\item Jonathan Jeurissen
				\item Sina Khakbaz Heshmati
				\item Bart Maes
				\item Jorne Laton
				\item Patrick Provinciael
				\item Wouter Van Rossem
			\end{itemize}
There were no members absent.
			
		\subsection{Revision History}
			\begin{tabular}{c | l | l }
				\textbf{Rev.} & \textbf{Date} & \textbf{Description} \\
				\hline
				1.0 & November 28, 2009 & First draft created \\

			\end{tabular}		

\section{Scope}

In order to report the current state of the \emph{Software Engineering} projects, a conference is organised on December 15 with all three teams. In a presentation of 30-45 minutes several aspects of the development should be treated, including statistics, innovation and a proof of concept. 

\section{Presentation schedule}

During meeting 9 on November 24, we did some brainstorming in order to be able to start organising the presentation. This led to the following schedule:

\begin{itemize}
	
	\item \textbf{Introduction} \\ Nick - 10 MIN
	\begin{enumerate}
		\item General introduction including scope of project
		\item Presentation of team and project
		\item Statistics and costs
		\item Deadlines and planning
	\end{enumerate}
	
	\item \textbf{Innovation and requirements} \\ Bart \& Wouter - 10 MIN
	\begin{enumerate}
		\item General overview of requirements
		\item Innovative aspects
		\item Look and feel of website by prototypes
		\item Vision on product
		\item Proof of concept
	\end{enumerate}
	
	\item \textbf{Configuration \& tools} \\ Jorne \& Sina - 6 MIN
	\begin{enumerate}
		\item General overview of tools
		\item Motivation of choices
	\end{enumerate}
	
	\item \textbf{Quality assurance guidelines} \\ Patrick - 4 MIN
	\begin{enumerate}
		\item Mechanisms to assure quality
	\end{enumerate}
	
	\item \textbf{Pitch} \\ Jonathan - 3 MIN
	\begin{enumerate}
		\item Summarize presentation
		\item Convince listeners of innovative aspects
		\item Make an impression
	\end{enumerate}
	
\end{itemize}
\\
In order to make the presentation more active, duo presentations were suggested. Having this, it's important for both speakers to interact with each other. 


\section{Next}

By Meeting 10 on December 1, every aspect of the presentation has to be elaborated in a more detailed way. Thereafter the slides that will be used during the presentation can be made.

		
\end{document}
