\documentclass{article}

\usepackage{hyperref}

\begin{document}

	\title{Software Engineering Group 2 (2009-2010) \\ Highlights February 2010}
	\author{Nick De Cooman}
	\date{\today}

\maketitle

This report aims to give an overview of recent improvements of the Salesmen Project. A more detailed view on the status of this project can be obtained by looking at the timesheets \cite{timesheets}. \\

After having examens, we resumed the development in February. This month we have been busy on:

\begin{itemize}
	
	\item \textbf{Holding an Evaluation} \\
	On February 15, a meeting was held to discuss the problems that were encountered during the first semester. Each team member was able to speak about the causes that prevented them from doing the work they were assigned to. Minutes of this meeting can be found on our project website \cite{eval}.
	
	\item \textbf{Hands-on Workshops} \\
	We introduced the concept of having workshops during which all team members can work collaboratively. This should increase the group spirit and allows to share knowledge in an  effecient way. 
	
	\item \textbf{Having Remote Server Up and Running} \\
	By having a daemon installed to ensure server uptime, we are able to present a demo \cite{demo} of the Salesmen project at all time. 

	\item \textbf{Programmed Some Basic Functionalities} \\
	Our demo website already provides some basis functionality. Among other things, visitors can do a basic search which returns the results asynchronously. 

\end{itemize}

\begin{thebibliography}{99}

	\bibitem{timesheets}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/timesheets/}{http://wilma.vub.ac.be/~se2_0910/docs/timesheets/}
	
	\bibitem{eval}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/minutes/2010/02/15/minutes-20100215.pdf}{http://wilma.vub.ac.be/~se2_0910/docs/minutes/2010/02/15/minutes-20100215.pdf}
	
	\bibitem{demo}
	\href{http://wilma.vub.ac.be:1388/salesmen/}{http://wilma.vub.ac.be:1388/salesmen/}	
\end{thebibliography}


\end{document}