\documentclass[a4paper, 12pt]{article}
\usepackage[english]{babel}
\usepackage{graphicx, ctable, url}
\usepackage{hyperref}
\usepackage{eurosym}
\usepackage{listings} % source listings
\lstloadlanguages{java}
\lstset{keywordstyle=\ttfamily\bfseries}
\lstset{flexiblecolumns=true}
\lstset{commentstyle=\ttfamily\itshape}

	\begin{document}

\title{Minutes Meeting 14}
\author{Wouter Van Rossem}
\date{\today}

\maketitle	
	\section{Meeting Information}
		\textbf{Date:} Friday, February 12, 2010\\
		\textbf{Time:} 10H00--11H40\\
		\textbf{Place:} D.3.13\\
		\subsection{Attendees}
Following members were present:
			\begin{itemize}
				\item Nick De Cooman
				\item Sina Khakbaz Heshmati
				\item Bart Maes
				\item Jorne Laton
				\item Patrick Provinciael
				\item Wouter Van Rossem
			\end{itemize}
Following members were absent:
			\begin{itemize}
			 	\item Jonathan Jeurissen
			\end{itemize}
			
\section{Evaluation}
	A meeting will be held to discuss what went right and what went wrong during the last semester. Each team member will be able to speak their minds about the problems they encountered that prevented them from doing the work they were assigned to do.

\section{Timesheets}
	Timesheets will now come online Monday evening. The deadline to submit timesheets is still Sunday 23h59.	
	
	In order for each member to get his full study points (and not exceed these), the workload for each member was calculated by Nick. Here is a short summary (the complete charts are also available \cite{graphs}):
	
	\begin{description}
		\item[Nick, Bart, Patrick]: 8 hour/week
		\item[Wouter, Jorne]: 9 hour/week
		\item[Sina, Jonathan]: 3 hour/week
	\end{description}
	
Wouter will also manage the website from now on, in order to reduce some of the workload of Sina. Configuration will now be completely done by Jorne as well.

\section{Planning}
	Nick created a planning for this semester, which was approved by all present members. The planning is as follows:
	
	\begin{description}
		\item[8/2 - 21/2]: Evaluation of the previous semester and preparation for the implementation phase
		\item[22/2 - 29/3]: Implementation phase. Also, preparation for the second conference during the last couple of weeks
		\item[Easter holiday]: Nothing
		\item[19/4 - 17/5]: Finish the implementation and prepare for the third conference
	\end{description}
	
	There will also be less meetings from now on. 

\section{Server and Database}
	There will be two versions of the salesmen project on the server: \textit{salesmen development} and \textit{salesmen stable}. This way a stable version of the site will always be available, while members can also still deploy their test code remotely. Patrick will be in charge of maintaining the stable branch. Patrick also suggested that we should evaluate this system after a couple of weeks.
	
\section{Communication}
	Google Wave was chosen as an additional communication channel. IRC was another option, but Wave was preferred by several members. 
			
		\subsection{Revision History}
			\begin{tabular}{c | l | l }
				\textbf{Rev.} & \textbf{Date} & \textbf{Description} \\
				\hline
				1.0 & Monday 15, 2010 & First draft created \\
				%1.1 & December 20, 2009 & Revised by QA Manager \\
				%1.2 & December 21, 2009 & Ready to be uploaded \\
			\end{tabular}		

	\section{}
	\section{Next Meeting}

		\textbf{Date:} Monday, February 16, 2010\\
		\textbf{Time:} 18H00--19H30\\
		\textbf{Place:} Infogroep\\
	
		\subsection{Agenda}
A complete list of Agenda items is available on \cite{agendaitems}.\\
	
	\begin{thebibliography}{99}
		
		\bibitem{agendaitems}
		\href{http://code.google.com/p/salesmen/wiki/NextMeetingTopics}{http://code.google.com/p/salesmen/wiki/NextMeetingTopics}

		\bibitem{graphs}
		\href{http://groups.google.com/group/salesmen/browse_thread/thread/5b99f469ae9ab3d7}{$http://groups.google.com/group/salesmen/browse_thread/thread/5b99f469ae9ab3d7$}
		
	\end{thebibliography}	
		
\end{document}
