\documentclass[a4paper, 12pt]{article}
\usepackage{ctable}
\usepackage{url}

\title{Software Engineering Group 2 - 2009-2010 
  \\ Meeting Minutes - October 16, 2009}
\author{Nick De Cooman}
\date{October 18, 2009}

\begin{document}
	
\maketitle

\begin{center}
  Meeting started at \emph{12h10} and ended at \emph{12h55} 
  (Duration: \emph{45 minutes}) \\
\end{center}

\section{Roll Call}

\begin{tabular}{l l}
  \large{\textbf{Attendees}} & \large{\textbf{Status}} \\
  Nick De Cooman & Present \\
  Jonathan Jeurissen & Present \\
  Sina Khakbaz Heshmati & Present \\
  Jorne Laton & Present \\
  Bart Maes & Present \\
  Patrick Provinciael & Present \\
  Wouter Van Rossem & Present \\
  \\
\end{tabular}	
	
\section{Team Members}

\begin{tabular}{l l}
		
  \FL Name & Studies
  \ML Nick De Cooman & Computer Science, 3rd Bachelor
  \NN Jonathan Jeurissen & Applied Science, 1st Master Electronics
  \NN Sina Khakbaz Heshmati & Computer Science, 3rd Bachelor
  \NN Jorne Laton & Applied Science, 3rd Bachelor Computer Science
  \NN Bart Maes & Computer Science, 3rd Bachelor
  \NN Patrick Provinciael & Computer Science, 3rd Bachelor
  \NN Wouter Van Rossem & Computer Science, 3rd Bachelor
  \LL
  \\
		
\end{tabular}	
	
\section{Members' strengths}
	
\begin{itemize}

\item Nick: CSS, HTML, Java, \LaTeX, SQL, XML
\item Jonathan: HTML, Java, Javascript  
\item Sina: CSS, CVS, Docbook, HTML, Java, Javascript, \LaTeX, GNU/Linux, 
  Subversion, SQL, XML, XSLT, Ant
\item Jorne: CSS, HTML, Java, Javascript, GNU/Linux
\item Bart: CSS, HTML, Java, Javascript, GNU/Linux, SQL, XML
\item Patrick: CSS, HTML, \LaTeX, SQL
\item Wouter: CSS, HTML, Java, Javascript, \LaTeX, GNU/Linux, SQL, XML 

\end{itemize}	
	
\section{Job Assignments}
	
Although we came to an agreement, the following assignments are temporary. 
The definitive decision will be made during the next meeting.

\begin{tabular}{l l l}
  \\
  \FL Role & Effective & Backup
  \ML Project Leader & Nick & Patrick
  \NN Configuration Manager & Jorne & Sina
  \NN Quality Assurance Manager & Patrick & Bart
  \NN Requirements Manager & Wouter & Jonathan
  \NN Design Manager & Bart & Nick
  \NN Implementation Manager & Sina & Jorne
  \LL
  \\
\end{tabular} 
	
\section{Website}
	
The website needs to be online as quickly as possible. As Sina has 
experience building websites, he will be responsable for publishing the 
website using SilkPage. Wouter will be the backup \emph{webmaster}.\\

\subsection{SilkPage}
SilkPage is an XML-based publishing tool that generates Web standards 
compliant websites. We chose this tool to maintain our project's website 
for the following reasons:

\begin{itemize}
\item Separation of concerns: We can focus on the website's content 
  and use semantic tags provided by the DocBook XML vocabulary; 
  everything else is taken care of by SilkPage.
\item Native support for publishing external documents in various formats.
  \cite{javad-resume} \cite{dixite-docs}
\item Customization layers: SilkPage can easily be extended at CSS and
  XSLT levels.
  \cite{silkpage-docs}

\end{itemize}


\section{Next Meeting}
Next meeting will be held on October 20, 2009 at 17h00.
\subsection{Agenda}
\begin{itemize}
\item Definitive decision about job assignments.
\item Demonstration and evaluation of our website.
\item Decide which language to use for publishing our reports.
\item Software Project Management Plan (SPMP).
\item Setup a project milestones (deadlines).
\item Risk Analysis.
\item Schedule the next meeting.
\end{itemize}
	

\begin{thebibliography}{9}
\bibitem{javad-resume}
  http://javad.khakbaz.com/whoami/resume/

\bibitem{dixite-docs}
  http://www.dixite.com/docs/
  
\bibitem{silkpage-docs}
  http://silkpage.markupware.com/docs/
  
\end{thebibliography}
	
\end{document}