\documentclass[a4paper, 12pt]{article}
\usepackage[english]{babel}
\usepackage{graphicx, ctable, url}
\usepackage{hyperref}
\usepackage{eurosym}
\usepackage{listings} % source listings
\lstloadlanguages{java}
\lstset{keywordstyle=\ttfamily\bfseries}
\lstset{flexiblecolumns=true}
\lstset{commentstyle=\ttfamily\itshape}

	\begin{document}

\title{Minutes Conference Meeting 3}
\author{Nick De Cooman}
\date{\today}

\maketitle	
	\section{Meeting Information}
		\textbf{Date:} Thursday, December 10, 2009\\
		\textbf{Time:} 17H15-18H15\\
		\textbf{Place:} E0.14\\
		
		\subsection{Attendees}
Following members were present:
			\begin{itemize}
				\item Nick De Cooman
				\item Jonathan Jeurissen
				\item Sina Khakbaz Heshmati
				\item Bart Maes
				\item Jorne Laton
				\item Wouter Van Rossem
			\end{itemize}
Patrick Provinciael was excused.
			
		\subsection{Revision History}
			\begin{tabular}{c | l | l }
				\textbf{Rev.} & \textbf{Date} & \textbf{Description} \\
				\hline
				1.0 & December 11, 2009 & First draft created \\

			\end{tabular}		

\section{Practice presentation}

After the meeting on December 08, certain slides changed drastically in order to improve the structure and content of the presentation. This meeting was held to get feedback on those adjustments. 

\begin{itemize}
	
	\item Project information:
	\begin{itemize}
		\item Small difference in font color 
	\end{itemize}
	
	\item Innovation and requirements:
	\begin{itemize}
		\item Structure much better, good interaction
		\item Wrong prototypes were included in slides
		\item Extra slide for proof on concept has to be added 
	\end{itemize}
	
	\item Tools and configuration:
	\begin{itemize}
		\item Part on JBoss and Seam was too detailed. 
		\item Reason why we have chosen for JBoss was missing.
		\item Presentation took too long (12MIN). 
		\item There has to be more interaction between speakers.
	\end{itemize}
	
	\item Recap
	\begin{itemize}
		\item Should more focus on requirements and innovation. 
	\end{itemize}
	
\end{itemize}


\section{Next}

Small adjustments to the slides can be made until December 11. The final slides will be available on December 12.

\end{document}
