\documentclass{article}

\usepackage{hyperref}

\begin{document}

	\title{Software Engineering Group 2 (2009-2010) \\ Highlights April 2010}
	\author{Nick De Cooman}
	\date{\today}

\maketitle

This report aims to give an overview of recent improvements of the Salesmen Project. A more detailed view on the status of this project can be obtained by looking at the timesheets \cite{timesheets}. \\

This month, we have been working on:

\begin{itemize}
	
	\item \textbf{Updating documents} \\
	After having iteration I completed, most of our documents were updated and lifted to a new version. The SPMP \cite{spmp} now contains up-to-date statistics and explains the main management decisions that were made. The SCMP \cite{scmp} is extended with the JBoss Seam architecture and covers all tools that we need to make use of it. Finally, the SQAP \cite{sqap} and STD \cite{std} were improved in order to give a clearer image about the quality and testing of the Salesmen project.
	
	\item \textbf{Assigning new tasks} \\
	On April 19, the main priorities for the final stage of this project were discussed and resulted in new implementing tasks. Those were distributed among all team members. 
	
	\item \textbf{Using Quartz} \\
	To be able to process a finished auction, we are making use of Quartz to discover the termination of an auctions. Seam also provides extra support for this.
	
	\item \textbf{Implementing} \\
	Our application is extented with extra functionality. Among other things, a user account is now blocked after a certain number of login attempts and a mechanism to handle finished auctions is provided.

\end{itemize}

\begin{thebibliography}{99}

	\bibitem{timesheets}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/timesheets/}{http://wilma.vub.ac.be/~se2_0910/docs/timesheets/}
	
	\bibitem{spmp}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/spmp/index.html}{http://wilma.vub.ac.be/~se2_0910/docs/spmp/index.html}
	
	\bibitem{scmp}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/scmp/index.html}{http://wilma.vub.ac.be/~se2_0910/docs/scmp/index.html}
	
	\bibitem{sqap}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/sqap/index.html}{http://wilma.vub.ac.be/~se2_0910/docs/sqap/index.html}
	
	\bibitem{std}
	\href{http://wilma.vub.ac.be/~se2_0910/docs/std/index.html}{http://wilma.vub.ac.be/~se2_0910/docs/std/index.html}
	
\end{thebibliography}


\end{document}