\chapter{Specific Requirements}

\section{Requirements Control Plan}
	This section describes how the different requirements will be described and how 
	modifications to these requirements will be handled. \\
	Each requirement will have a unique identifier which will be used for referencing 
	in the source code, the design, ... Some requirements will only be described by
	a short description, while others will be described by a use case. \\
	Whenever a requirement changes, the change will be noted at the description of 
	the requirement. If a requirement is retired, this will also be noted at the
	requirement description, together with a reason why the requirement was retired.

%\section{External Interface Requirements}

\input{functional-requirements}

\input{nonfunctional-requirements}

%\section{Performance Requirements}
\section{Database Requirements}
	All data will be saved in the database. The database must always remain consistent. There will be many concurrent request 
	for the database. A good database structure will be needed. 
\section{Design Constraints}
	\begin{enumerate}
		\item The design must be object-oriented
		\item Design diagrams must be made using UML
	\end{enumerate}
\section{Software system attributes}
	\subsection{Reliability}
		Errors in the code will be divided into 2 groups: \textit{small errors} and \textit{fundamental errors}. \\ 
		Fundamental errors will be corrected within 48 hours after the detection of this error. Small errors (details) will be corrected within a week after the detection of these errors. 
%	\subsection{Availability}
	\subsection{Security}
		\begin{itemize}
			\item When a user want to recover his or her password, the site will generate a new password and send it to the user's e-mail.
			\item Communication of sensitive data should be encrypted (e.g. using https)
			\item Users should only be allowed to try to log in a limited number of times
			\item When a guests registers for an account, he or she has to fill in a CAPTCHA
		\end{itemize}
%	\subsection{Maintainability}
%	\subsection{Portability}
%\section{Other Requirements}
\section{Summary}
	\begin{tabular}{|c|c|c|}	
		\hline \textbf{Must have} & \textbf{Want to have} & \textbf{Nice to have} \\ 
		\hline  Create new account & Search a user & View recommended auctions \\ 
		\hline  Log in & View active auctions & Send a personal message \\ 
		\hline  Search for an auction & View placed auctions & View personal messages \\
		\hline  View auctions of a category & Follow an auction & Delete a personal message \\ 
		\hline  Log out & View salespal & Add seller to favourites \\ 
		\hline  Place an auction & Top up salespal & View favourite sellers \\ 
		\hline  Bid on an auction & View buyer's assistant &  Delete a favourite seller\\ 
		\hline  Modify account information & Comment on an auction & Extra site for banned users \\ 
		\hline  Retrieve password & Change currency & Advanced e-mail notification \\ 
		\hline  Remove a user & View auctions with a tag &  \\ 
		\hline  Remove an auction & Cookies &  \\ 
		\hline  Change language & View followed auctions &  \\ 
		\hline  CAPTCHA & View transaction &  \\ 
		\hline  Limited login attempts & Pay transaction  &  \\ 
		\hline  Encrypted password & Rate transaction  &  \\
		\hline  Browser compatibility & Retract bid  &  \\
		\hline  Secure connection & Basic e-mail notification &  \\
		\hline  & Confirm account &  \\
		\hline  & Request new confirmation mail &  \\
		\hline
	\end{tabular} 