%Type document, past een aantal dingen aan. Kort = article, lang = report
\documentclass[a4paper, 12pt]{report}
% Om afkappingstekens op de juiste plaats te zetten
\usepackage[english]{babel}
%Graphicx is voor mooie afbeeldingen, ctable is voor tabellen, url is om links te maken naar internet.
\usepackage{graphicx, ctable, url}
%hyperref is om links binnen uw documenten te leggen, bijvoorbeeld van de bibliografie
\usepackage{hyperref}

%Dit is om source listings te gebruiken, voor meer details lees ftp://ftp.tex.ac.uk/tex-archive/macros/latex/contrib/listings/listings.pdf (gezien je dit later ook vak zal gebruiken)
\usepackage{listings} % source listings
\lstloadlanguages{java}
\lstset{keywordstyle=\ttfamily\bfseries}
\lstset{flexiblecolumns=true}
\lstset{commentstyle=\ttfamily\itshape}

%begint het eigenlijke document
\begin{document}

%geeft titel een naam
\title{Software Requirements Specification}
%Naam van de schrijver
\author{Wouter Van Rossem}
%Date kan ook gebruikt worden als Version History
%\date{	1 November , 2009: First draft }
\maketitle
\begin{center}
	\textbf{Abstract} \\
	This document describes the Software Requirements Specifications for
	the software behind an online auction website This project is part of 
	the course on software engineering at the Vrije Universiteit Brussel.
	
\end{center}
%Table of revisions here
\tableofcontents

\chapter{Introduction}
\section{Purpose}
	The purpose of this document is to present an overall description and 
	listing of the functionality of the system behind an online auction 
	website. This document is intended for users of the system including
	designers, testers, implementation unit and the employer.
\section{Scope}
	Salesmen is the system behind an online auction website. An auction site 
	is a web application where users can buy and sell objects. Users can 
	place auctions or bid on auctions of other users. 
\section{Definition And Abbreviation}
	\begin{itemize}
		\item \emph{SRS}: Software Requirements Specification
		\item \emph{UML}: Unified Modelling Language
		%\item \emph{}:
	\end{itemize}
\section{Reference}
\section{Overview}
	Section 2 describes the general factors that affect the product and 
	its requirements.                                                                                   
	This section does not state specific requirements. Instead, it provides a 
	background for those requirements, which are defined in detail in Section 
	3 of the SRS, and makes them easier to understand.\\
	Section 3 contains all of the software requirements, to a level of detail 
	sufficient to enable designers to design the system to satisfy these 
	requirements, and testers to test that the system satisfies these
	requirements.

\chapter{Overall Description}

\section{Product Perspective}
	The project will make use of a database and a web server that can be 
	accessed with any web browser.
\section{User Characteristics}
	The users of the system will be users with different levels of 
	technical expertise. Any user with a basic understanding of the 
	internet and auctions should be able to make use of all the 
	available functionality of the system.\\
	There are three different types of users:
	\begin{itemize}
		\item \textbf{Guests}: These are visitors of the site which don't 
		have an account yet or aren't logged in.
		\item \textbf{Member}: These are users of the site who have an 
		account and are logged in.
		\item \textbf{Administrators}: These are special members of the 
		site who manage the site.
	\end{itemize}
\section{Interfaces}
	\subsection{User interfaces through forms}
	\textbf{Account information} \\
		\begin{itemize}
			\item Username (mandatory)
			\item Password (mandatory)
			\item Password verification (mandatory)
			\item E-mail (mandatory)
			\item E-mail verification (mandatory)
			\item Default Language
		\end{itemize}
	\textbf{Personal information}
		\begin{itemize}
			\item First Name (mandatory)
			\item Last Name (mandatory)
			\item Address (optional)
			\item Phone number (optional)
			\item Date of birth (mandatory, minimum 18 years old)
		\end{itemize}
	\textbf{Registration form}
		\begin{itemize}
			\item Account information (mandatory)
			\item Personal information (mandatory)
		\end{itemize}
	\textbf{Login form}
		\begin{itemize}
			\item Username
			\item Password
		\end{itemize}
	\textbf{Auction search form}
		\begin{itemize}
			\item Auction name
		\end{itemize}
	\textbf{Member search form}
		\begin{itemize}
			\item Member name
		\end{itemize}
	\textbf{Place auction form}
		\begin{itemize}
			\item Auction name
			\item Transport options
			\item Minimum price
			\item Duration
			\item Auction type
			\item Category
			\item Tags
			\item Other information
		\end{itemize}
	\textbf{Bidding form}
		\begin{itemize}
			\item Mamximum offer
		\end{itemize}
\section{Product Functions}
	\subsection{Guest}
		Guests can
		\begin{itemize}
			\item Browse through auctions
			\item Request an account
			\item Log in
		\end{itemize}
	\subsection{Member}
		Members can
		\begin{itemize}
			\item Browse through auctions
			\item Place auctions
			\item Bid on auctions
			\item Access and change their account information
			\item Contact other users
		\end{itemize}
	\subsection{Administrator}
		Administrators can
		\begin{itemize}
			\item Manage the members
			\item Manage the auctions
		\end{itemize}
\section{Constraints}
\begin{itemize}
	\item The system must work on Linux, and more specifically on Wilma
	\item The design should be modular, so extensions and replacements of 
	modules will be simplified
	\item The web interface should be simple, attractive and standard
	(CSS, XHTML)
	\item The basic programming language must be Java
	\item Only open source software and libraries may be used
\end{itemize}
%\section{Assumptions and Dependencies}
\section{Apportioning of Requirements}
	In order to have a working prototype available at the end of the
	first iteration, some functionality have different priorities.
	\begin{itemize}
		\item \textbf{Must have}: These functionalities should definitely 
		be in the system, preferably after the first iteration.
		\item \textbf{Want to have}: These functionalities should be in 
		the system, but could be dropped when there isn't enough time.
		\item \textbf{Nice to have}: These functionalities should only be 
		implemented if all the 'must have' and 'want to have' 
		requirements are implemented and there is still some time left.
	\end{itemize}

\chapter{Specific Requirements}

%\section{External Interface Requirements}
\section{Functional Requirements} % Organized by user class
% Template
%\subsubsection{Remove an auction}
%			\begin{description}
%				\item[Priority]
%				\item[Actor]
%				\item[Preconditions]
%				\item[Description]
%				\item[Exceptions]
%				\item[Result]
%			\end{description}
	\subsection{Guest}
		\subsubsection{Create a new account}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Guest
				\item[Preconditions] User is not logged in
				\item[Description]
				A guest can create a new account so that he or she 
				can use the full functionality of the site
 				\item[Path]
 					\begin{enumerate}
						\item Guest selects \emph{register}
						\item Guest fills in \emph{registration form}
						\item Guest submits form
						\item System checks form and if valid saves it
						\item System send a confirmation mail 
					\end{enumerate}
				\item[Exceptions]
					\begin{enumerate}
						\item Username is already taken
						\item Incorrect information in the registration form
					\end{enumerate}
				\item[Result] An account is created for the user
			\end{description}
		\subsubsection{Log in}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Guest
				\item[Preconditions] The user is registered on the site.
				User is not logged in.
				\item[Description]
				If a user is registered but not logged in, he or she can
				log in to use the full functionality of the site.
				\item[Path]
 					\begin{enumerate}
						\item Guest fills in login form
						\item Guest submits form
						\item System checks if the form is valid and if so logs
						the user in
					\end{enumerate}
				\item[Exceptions]
					\begin{enumerate}
						\item Incorrect username and or password
					\end{enumerate}
				\item[Result] The user is logged in
			\end{description}
	\subsection{Guest and Member}
		\subsubsection{Search for an auction}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Member or Guest
				\item[Preconditions] User is at the home page
				\item[Description] Guests and members can search for auctions
				\item[Path]
 					\begin{enumerate}
						\item Users enters a search term in the search field
						\item User submits the search
						\item System returns all found auctions that match this search
						query
					\end{enumerate}
				\item[Exceptions] None
				\item[Result] The found auctions for the search term
			\end{description}
	\subsection{Member}
		\subsubsection{Log out}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Member
				\item[Preconditions] Member is logged in
				\item[Description] Members who are logged in can log out
				\item[Path]
 					\begin{enumerate}
						\item Member selects \emph{log out}
						\item System logs the member out
					\end{enumerate}
				\item[Exceptions] None
				\item[Result] The member is logged out
			\end{description}
		\subsubsection{Search a user}
			\begin{description}
				\item[Priority] Want to have
				\item[Actor] Member
				\item[Preconditions] User is at advanced search page
				\item[Description] Members can search for other members 
				\item[Path]
 					\begin{enumerate}
						\item Member enters search term in search member field
						\item Member submits search
						\item System returns all users corresponding to that search 
						query
					\end{enumerate}
				\item[Exceptions] None
				\item[Result] The found members for the search term
			\end{description}
		\subsubsection{Place an auction}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Member
				\item[Preconditions] Member is logged in. User is at home page or user home
				\item[Description] Members of the site can create a new auction on which
				other members can bid
				\item[Path]
 					\begin{enumerate}
						\item User selects \emph{place auction}
						\item User fills in \emph{new auction form}
						\item User submits the form
						\item System checks the form and if valid creates the auction
					\end{enumerate}
				\item[Exceptions] Incorrect information in the form, incomplete form
				\item[Result] Auction is placed
			\end{description}
		\subsubsection{Bid on auction}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Member
				\item[Preconditions] 
 					\begin{enumerate}
						\item User is logged in
						\item User is on an auction page
						\item Auction is not of the user
					\end{enumerate}
				\item[Description] Members can bid on auctions of other members
				\item[Path]
 					\begin{enumerate}
						\item User select \emph{bid}
						\item User fills in bidding form
						\item User submits form
						\item System checks form and if valid places the bid
					\end{enumerate}
				\item[Exceptions] Wrong bid value in the form, incomplete form
				, not enough credit on salespal account
				\item[Result] The bid is placed on the auction
			\end{description}
		\subsubsection{Modify account information}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Member
				\item[Preconditions] User is logged in. User is at control panel
				\item[Description] Members can modify their account information
				\item[Path]
 					\begin{enumerate}
						\item User selects \emph{modify account}
						\item User changes account information form
						\item User submits the form
						\item System checks the form and if valid, makes the changes
					\end{enumerate}
				\item[Exceptions] Incorrect information, incomplete form
				\item[Result] The account information of the user is changed
			\end{description}
		\subsubsection{Send a personal message to another member}
		\subsubsection{Follow an auction}
		\subsubsection{View Transaction}
		\subsubsection{Pay transaction}
		\subsubsection{Rate transaction}
		\subsubsection{Top-up salespal}
		\subsubsection{View salespal}
		\subsubsection{Add seller to favourites}
	\subsection{Administrator}
		\subsubsection{Remove a user}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Administrator
				\item[Preconditions] User is at control panel
				\item[Description] User selects \emph{manage users} and selects a user from the users list.
				After the user is selected, \emph{remove user} is selected.
				\item[Exceptions] None
				\item[Result] A user is removed from the system
			\end{description}	
		\subsubsection{Remove an auction}
			\begin{description}
				\item[Priority] Must have
				\item[Actor] Administrator
				\item[Preconditions] User is at control panel
				\item[Description] User selects \emph{manage auctions} and selects an auction from the auctions 
				list. After the auction is selected, \emph{manage auction} is selected.
				\item[Exceptions] None
				\item[Result] Auction is removed
			\end{description}	
%\section{Performance Requirements}
\section{Database Requirements}
	All data will be saved in the database. The database always remain consistent. There will be many concurrent request 
	for the database. A good database structure will be needed. 
\section{Design Constraints}
	\begin{enumerate}
		\item The design must be object-oriented
		\item Design diagrams must be made using UML
	\end{enumerate}
%\section{Software system attributes}
%	\subsection{Reliability}
%	\subsection{Availability}
%	\subsection{Security}
%	\subsection{Maintainability}
%	\subsection{Portability}
%\section{Other Requirements}

%\chapter{Additional Materials}

\end{document}