\documentclass[a4paper, 12pt]{article}
\usepackage[english]{babel}
\usepackage{graphicx, ctable, url}
\usepackage{hyperref}
\usepackage{eurosym}
\usepackage{listings} % source listings
\lstloadlanguages{java}
\lstset{keywordstyle=\ttfamily\bfseries}
\lstset{flexiblecolumns=true}
\lstset{commentstyle=\ttfamily\itshape}

	\begin{document}

\title{Minutes Conference Meeting}
\author{Nick De Cooman}
\date{\today}

\maketitle	
	\section{Meeting Information}
		\textbf{Date:} Monday, March 29, 2010\\
		\textbf{Time:} 14H00-16H00\\
		\textbf{Place:} 5F212
		
		\subsection{Attendees}
Following members were present:
			\begin{itemize}
				\item Nick De Cooman
				\item Sina Khakbaz Heshmati
				\item Bart Maes
				\item Wouter Van Rossem
			\end{itemize}
			
		\subsection{Revision History}
			\begin{tabular}{c | l | l }
				\textbf{Rev.} & \textbf{Date} & \textbf{Description} \\
				\hline
				1.0 & March 31, 2010 & First draft created \\
				2.0 & April 02, 2010 & Revision after QA \\

			\end{tabular}
			\\		

\section{Scope}

In order to report the current state of all three \emph{Software Engineering} projects, a conference is held on March 31. In a presentation of 30 minutes several aspects of the development should be highlighted, including management information and a demo. This meeting is held to finalize the slides and to determine a demo scenario. 

\section{Implementation progress}

The slides about the implementation progress were made collaboratively. Moreover, we discussed that the focus should be on the fact that JBoss Seam makes the development slow due to a steep learning curve, but that it returns a lot of power and flexibility at the same time. 

\section{Demo}

To be able to present a smooth demo, a scenario was written down. It treats the following subjects:
\begin{itemize}
	\item User registration
	\item Email service
	\item Language support
	\item User space
	\item Search engine
	\item Placing auctions
\end{itemize}


\section{Management information}

All slides about the management information were discussed. In general, only some minor changes have to be made. For instance, statistics about weekly averages are not significant and should therefore be removed from the slides.  



\section{Next meeting}

By having all slides ready now, the presentation can be rehearsed. This will be done in an extra conference meeting on Tuesday March 30, 2010 at 16h.

		
\end{document}
