\documentclass{article}
\begin{document}


\section{Introduction}
	The purpose of this document is to give an explanation about the Software Configuration Management, which regulates the storage of all project files.


\section{Management}
	\subsection{Organization}
		Configuration Manager: Jorne Laton\n
		Assistant Configuration Manager: Sina Khakbaz Heshmati
	\subsection{Responsibilities}
		\begin{itemize}
			\item Organizing the Software Configuration Management
			\item Writing and maintaining the SCMP
			\item Installing and maintaining tools
			\item Supporting users of these tools
		\end{itemize}


\section{Configuration}
	\subsection{Configuration Tree}
		\begin{description}
			\item[trunk]
				Main directory of the project
				\begin{description}
					\item[docs]
						SPMP and SCMP.
					\item[utils]
						Utilities.
					\item[www]
						Images, source code, configuration files of the website.
				\end{description}
			\item[branches]
				Previous stable versions of the project.
			\item[minutes]
				Reports of meetings.
			\item[timesheets]
				Each member's timesheet per week.
			\end{description}
	\subsection{Tools}
		\begin{description}
			\item[XML:]
				Each project member writes his timesheet in XML-format. These files are then compiled to readable text to put on the website.
			\item[\LaTeX{}:]
				All documents are written in \LaTeX{}, SPMP, SCMP, Minutes, etc.
			\item[Google Code]
				Google Code has been chosen as the server for all our files.
			\item[SVN]
				Subversion has been chosen to checkout, commit or update files from or to the Google Code server.
		\end{description}
	\subsection{Control}
	All team members can access items on the server, using the checkout or the update command, so that everyone is able to have a working copy of the original file on his computer.
	Edits can only be made to the working copy and, when finished editing, then committed back to the server.
	When this is done the server will save these changes in a new revision, incrementing the revision index.


\end{document}
