\documentclass[a4paper, 12pt]{article}
\usepackage{ctable}
\usepackage{url}

\title{Software Engineering Group 2 (2009-2010) \\Pre-meeting Report - October 16, 2009}
\author{Nick De Cooman}
\date {Meeting started at 12H10}

\begin{document}
	
	\maketitle
	
	\begin{tabular}{l l}
		{\large \textbf{Attendees}} \\
		Nick De Cooman & Present \\
		Jonathan Jeurissen & Present \\
		Sina Khakbaz Heshmati & Present \\
		Jorne Laton & Present \\
		Bart Maes & Present \\
		Patrick Provinciael & Present \\
		Wouter Van Rossem & Present \\
		\\
	\end{tabular}	
	
	\section{Team Members}
	
	\begin{tabular}{l l}
		
		\FL Name & Studies
		\ML Nick De Cooman & Computer Sciences, 3th Bachelor
		\NN Jonathan Jeurissen & Engineering Sciences, 1st Master Electronics
		\NN Sina Khakbaz Heshmati & Computer Sciences, 3th Bachelor
		\NN Jorne Laton & Engineering Sciences, 3th Bachelor Computer Sciences
		\NN Bart Maes & Computer Sciences, 3th Bachelor
		\NN Patrick Provinciael & Computer Sciences, 3th Bachelor
		\NN Wouter Van Rossem & Computer Sciences, 3th Bachelor
		\LL
		\\
		
	\end{tabular}	
	
	\section{Members' strengths}
	
	\begin{itemize}
		
		\item Nick: CSS, (X)HTML, Java, \LaTeX, SQL, XML
		
		\item Jonathan: HTML, Java, Javascript
		
		\item Sina: CSS, CVS, Docbook, (X)HTML, Java, Javascript, \LaTeX, Linux, Subversion, 
		SQL, XML, XMLT
		
		\item Jorne: CSS, (X)HTML, Java, Javascript, Linux
		
		\item Bart: CSS, (X)HTML, Java, Javascript, Linux, SQL, XML
		
		\item Patrick: CSS, (X)HTML, \LaTeX, SQL
		
		\item Wouter: CSS, (X)HTML, Java, Javascript, \LaTeX, Linux, SQL, XML 
		
	\end{itemize}	
	
	\section{Job Assignments}
	
	Although we came to an agreement, the following assignments are temporary. 
	The definitive decision will be made next meeting. 
	
	\begin{tabular}{l l l}
		\\
		\FL Role & Effective & Backup
		\ML Project Leader & Nick & Patrick
		\NN Configuration Manager & Jorne & Sina
		\NN Quality Assurance Manager & Patrick & Bart
		\NN Requirements Manager & Wouter & Jonathan
		\NN Design Manager & Bart & Nick
		\NN Implementation Manager & Sina & Jorne
		\LL
		\\
	
	\end{tabular} 
	
	\section{Website}
	
	The website needs to be as quickly online as possible. 
	Because Sina has the most experience with building websites,
	he will be responsable for this. Wouter will be the backup.
	
	We decide to build a site using SilkPage. This is an XML-based publishing tool 
	that generates Web standards compliant websites. 
	We chose this to maintain our project's website for the following reasons.

	\begin{itemize}
		
		\item Separation of concerns: We can focus on the website's content 
		and use semantic tags provided by the DocBook XML vocabulary; 
		everything else is taken care of.
		\item Native support for publishing external documents in various formats.
		\cite{site1} \cite{site2}
		\item Customization layers: SilkPage is easily extensible in both CSS and XSLT level.
		\cite{site3}

	\end{itemize}
	
	\section{Next Meeting}
	
	Next meeting will be on October 20, 2009 at 17H00. 
	
	\subsection{Agenda}
	
	\begin{itemize}
	
		\item Definitive decision about job assignments
		
		\item Demonstration of website and evaluation
		
		\item Decide on which language our reports will be written. 
		
		\item Software Project Management Plan (SPMP)
		
		\item Decide on deadlines
		
		\item Risk Analysis
		
		\item Scheduling next meeting 
		
	\end{itemize}
	
	
	\begin{center}
	 	Meeting ended at 12H55
	\end{center}	
	
	\begin{thebibliography}{99}
		
		\bibitem{site1}
		http://javad.khakbaz.com/whoami/resume/
		
		\bibitem{site2}
		http://java.khakbaz.com/docs/
		
		\bibitem{site3}
		http://silkpage.markupware.com/docs/
		
	\end{thebibliography}	
	
\end{document}