\documentclass[a4paper, 12pt]{article}
\usepackage[english]{babel}
\usepackage{graphicx, ctable, url}
\usepackage{hyperref}
\usepackage{eurosym}
\usepackage{listings} % source listings
\lstloadlanguages{java}
\lstset{keywordstyle=\ttfamily\bfseries}
\lstset{flexiblecolumns=true}
\lstset{commentstyle=\ttfamily\itshape}

	\begin{document}

\title{Minutes Conference Meeting}
\author{Nick De Cooman}
\date{\today}

\maketitle	
	\section{Meeting Information}
		\textbf{Date:} Tuesday, March 30, 2010\\
		\textbf{Time:} 16H00-17H00\\
		\textbf{Place:} E1.002
		
		\subsection{Attendees}
Following members were present:
			\begin{itemize}
				\item Nick De Cooman
				\item Sina Khakbaz Heshmati
				\item Wouter Van Rossem
			\end{itemize}
			
		\subsection{Revision History}
			\begin{tabular}{c | l | l }
				\textbf{Rev.} & \textbf{Date} & \textbf{Description} \\
				\hline
				1.0 & March 31, 2010 & First draft created \\
				2.0 & April 02, 2010 & Revision after QA \\
				3.0 & April 05, 2010 & Revision of section 3 after remark Sina

			\end{tabular}	
			\\	

\section{Scope}

In order to report the current state of all three \emph{Software Engineering} projects, a conference is held on March 31. In a presentation of 30 minutes several aspects of the development should be highlighted, including management information and a demo. This meeting is used to rehearse the final presentation. 

\section{Implementation progress}

The presentation may not be too technical, and should mainly cover the progress of the implementation and the obstacles that were encountered. Also multiple concrete examples should be given to allow the listener to fully understand why the development is progressing so slow. During the rehearsal, it appeared that Sina should rehearse his presentation in Dutch a bit more for the conference.

\section{Demo}

The presentation and demo are going to be on the same laptop, so it was practised how to switch smoothly. 


\section{Management information}

The rehearsal of the management information slides was more or less fluently, only the ending should be more convincing. 


\section{Final rehearsal}

On March 31 at 12H, the demo scenario will be rehearsed a final time to make sure that everything works as it should be. 



		
\end{document}
